
\documentclass{article}

\pagestyle{empty}

\addtolength{\topmargin}{-20mm}
\addtolength{\textheight}{40mm}
\addtolength{\oddsidemargin}{-28mm}
\addtolength{\textwidth}{50mm}

\begin{document}

\centerline{\bf\large CURRICULUM VIT\AE}

\vspace{3mm}

\centerline{\bf Rodion~N.~D\'eev}

\begin{description}

\vspace{1mm}

\item {\bf Personal data:}  Born in Saratov, Russian Federation, July 7, 1995. 
Citizenship: Russian Federation. Married,  no children.
\vspace{1mm}

\item {\bf Work mailing address:} \'Sniadeckich 8,  Warszawa,  Polska 00-656
\vspace{1mm}

%\item[Home address:] 2ya Sadovaya ul. 65/71-11, Saratov, Russia,
%410052.

\item {\bf E-mail:} {\tt rdeev[]impan.pl}
\vspace{1mm}

\item {\bf Telegram:} {\tt t.me/deevrod}
\vspace{1mm}

\item {\bf Contact phone number:} +48-573-373-834
\vspace{1mm}

\item {\bf Education:} \begin{itemize}
     \item 2021 \hspace{2mm} Ph.D. in Math. \hspace{2mm} Courant
     Institute of Mathematical Sciences~-- New York University
     \item 2016 \hspace{2mm} B.S. \hspace{2mm} National Research
     University~-- Higher School of Economics
\end{itemize}
\vspace{1mm}

\item {\bf Positions held:} \begin{itemize}
     \item Mar.~2024 (?)---Mar.  2025 \hspace{2mm} Universit\'e Libre de Bruxelles,  postdoc
     \item Oct.~2021---Sep.~2023 \hspace{2mm} Institite of Mathematics,  Polish Academy of Sciences,  postdoc
     \item Sep.~2016---Apr.~2021 \hspace{2mm} Courant Institute of Mathematical Sciences,
     graduate student
     \item Mar.~--- Aug.~2016 \hspace{2mm} Laboratory of Algebraic Geometry
	and Its Applications, research intern
     \item Nov.~2015---Apr.~2021 \hspace{2mm} Independent University of Moscow,
     graduate student
\end{itemize}

%\item[Short-term visiting positions:] \begin{itemize}
%\end{itemize}
\vspace{1mm}

\item {\bf Conferences:} \begin{itemize}
\item Apr.~--- May 2016,  Warsaw,  IMPAN,  Polish Algebraic Geometry Mini-Semester
\item Jul.  2022,  Gda\'nsk,  Fourth Killing--Weierstrass Colloquium
\end{itemize}

%\item[Awards:] \begin{itemize}
     %\item MacCracken Fellowship (2016)
%     \item Golden HSE Award, nomitation ``Silver Nestling'' (2015)
%     \item M\"obius contest (2015), 3rd prize
%     \item All-Russian Mathematical Olympiad (2010 and 2011), 2nd prize 
%\end{itemize}
\vspace{1mm}

\item {\bf Papers and preprints:} \begin{itemize}
     \item Rodion N. D\'eev. {\em 
     Compact fibrations with hyperk\"ahler fibers} (2015), J.~of~Geo.~\& Phys., 
     Vol.~123, Jan.~2018, pp.~372--378, arXiv:1511.05332.
     \item Rodion N. D\'eev. {\em
     Cousin groups and Hodge structures} (2016), arXiv:1610.06263.
     \item rodion~n.~d\'eev. {\em Haupt--Kapovich theorem revisited} (2020),
     arXiv:2010.15359.
     \item Fedor Bogomolov, Rodion D\'eev, Misha Verbitsky. {\em 
     Sections of Lagrangian fibrations on holomorphically symplectic manifolds 
     and degenerate twistorial deformations} (2020),  Advances in Mathematics, 
     Vol.  405,  27 Aug.  2022,  108479,  arXiv:2011.00469.
     %\item Rodion D\'eev,  Vasily Rogov.  {\em Holomorphic families of knots},  in 
     %preparation
     \item Anna Abasheva,  Rodion D\'eev.  {\em Complex surfaces with many 
     algebraic  structures} (2023),  IMRN 2023;  rnad190,  
     \url{https://doi.org/10.1093/imrn/rnad190},  arXiv:2303.10764
     \item Rodion D\'eev,  Micha\l~Kapustka.  {\em Rational curves with unexpected
     behaviour},  in preparation
\end{itemize}
\vspace{1mm}

\item {\bf Research interests:} transcendental methods in algebraic geometry, 
Teichm\"uller theory, holomorphically symplectic manifolds, Hodge theory, 
special holonomy, history of mathematics.

\end{description}
\end{document}
